Soundness Proofs for Iterative Deepening

### 2016-03-24 oopsla-16/proof/di.tex
Import proof
Fix definitions in proof for oopsla crowd

@@

The same as in the paper, we distinguish between data-race {\em candidates} and data-race {\em bugs}.
In this proof we are concerned solely with candidates, and wheter they can be observed to race or are false positives.
It is up to the MC to decide whether true data races are benign or buggy.

@@

These can immediately be identified as failures by a MC which tracks allocation state.
%Most commonly this refers to accesses to a region already freed, but for brevity we also include
% TODO: need heap block overrun?

>>>>

In our main paper, we refer to this relation as Limited HB.

@@

The same as in the paper, we distinguish between data-race {\em candidates} (or {\em potential} data races) and data-race {\em bugs}.
For brevity, we now use ``data race'' to refer both to true races and to potential data-race candidates identified by MHB.
In this proof we are concerned solely with candidates, and whether they can be observed to race or are false positives.
It is up to the MC to decide whether true data races are benign or buggy.

@@

These can immediately be identified as failures by a MC which tracks allocation state.
%Most commonly this refers to accesses to a region already freed, but for brevity we also include
